---
title: "News Topic Modeling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This markdown document contains R code for processing *news_table.csv*. The R code processes the article titles further in order to represent them using the [vector space model (VSM)](https://en.wikipedia.org/wiki/Vector_space_model).

```{r, message=FALSE, warning=FALSE}
library(tm)
library(tidyverse)
```


```{r}
titles_df <- read.csv("news_table.csv", stringsAsFactors = FALSE)
titles <- titles_df$title 
head(titles)
```

Text processing pipeline 

```{r}
titles %>%
  tolower %>%
  removePunctuation %>%
  removeWords(stopwords("en")) %>%
  map(function(x) gsub("[\r\n\t]", "",x)) ->
titles

head(titles)
```

Before getting term document matrix I'm going to take a quick detour here and look at what the most common words are

```{r}
words <- paste0(titles, collapse = " ")
words <- unlist(strsplit(words, " "))

head(words, 20)
```

```{r}
words <- words[words != ""]
head(words, 20)
```

```{r}
word_freqs <- words %>% 
                    table %>% 
                    sort(decreasing = TRUE) %>% 
                    data.frame(stringsAsFactors = FALSE)
names(word_freqs) <- c("word","freq")
glimpse(word_freqs)
head(word_freqs)
```

```{r}
ggplot(data = word_freqs[1:25,],
       aes(x=word, y=freq)) + 
       geom_bar(stat = "identity") +
       theme(
          axis.title = element_text(size = 14),
          axis.text = element_text(angle = 40, size=12),
          axis.title.y = element_text(size = 14),
          axis.text.y = element_text(size = 12)) +
       ggtitle("Word frequencies from news article title scrape (4/3/2017)") + 
       xlab("Words") + ylab("Frequency")
```

#### Back to more processing of text

```{r}
news_docs <- VectorSource(titles)

news_corpus <- Corpus(news_docs)
news_corpus
```

### Need to get site names

This might be better specified in the crawler script

```{r}
titles_df$site <- gsub("^.*www.", "", titles_df$link)
titles_df$site <- gsub(".com.*", "", titles_df$site)
head(sort(table(titles_df$site), decreasing = TRUE), 15)
```

